Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-11-27 paper/Interpreting Random Forest Predictions for Firearm Identification Using LIME.Rmd
worked on adding bin_continuous = FALSE options to the app - still some problems to fix :(

@@

  # Specify the options to use with lime 
  hamby224_lime_cases <- data.frame(bin_continuous = rep(TRUE, 18),
                                    quantile_bins = c(rep(TRUE, 9), rep(FALSE, 9)),
                                    nbins = rep(2:10, 2),
                                    use_density = rep(NA, 18)) %>%
  mutate(case = 1:length(nbins)) %>%
  select(case, bin_continuous, nbins, quantile_bins, use_density)

@@

@@

```{r}
# Specify the options to use with lime 
hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
                                      quantile_bins = rep(TRUE, 2),
                                      nbins = rep(4, 2),
                                      use_density = c(TRUE, FALSE)) %>%
  mutate(case = 1:length(nbins)) %>%
  select(case, bin_continuous, nbins, quantile_bins, use_density)

# Run the lime functions for the specified number of bins
hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
           .f = run_lime, # run_lime is one of my helper functions
           train = hamby173and252_train %>% select(rf_features),
           test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
           rfmodel = as_classifier(rtrees),
           label = "TRUE",
           nfeatures = 3)

# Separate the lime and explain function results
hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
```

@@

```{r}
hamby224_lime_results %>%
  ggplot(aes(x = nbins, y = mse, color = quantile_bins, group = quantile_bins)) +
  geom_point() + 
  geom_line() + 
  facet_grid( ~ set) + 
  theme_bw()
```

@@

Ideas for improvement of LIME: 
  - change the binning method:
    - lime is not good with linear relationships with classifiers due to the 
    inside-outside binning - it would be better to use a cumulative approach
  - consider interactions in the ridge regression model
  - learn lambda in the ridge regression

>>>>

Note: I realized that if `bin_continuous = FALSE`, then bins are not used at all. Instead, a kernel density estimator is used to sample from the distribution (or a normal distribution if specified), and then the ridge regression models are fit without "numerified" values.

@@

  # Specify the options to use with lime 
  hamby224_lime_cases <- data.frame(bin_continuous = c(rep(TRUE, 10), rep(FALSE, 2)),
                                    quantile_bins = c(rep(TRUE, 5), rep(FALSE, 5), rep(TRUE, 2)),
                                    nbins = c(rep(2:6, 2), rep(4, 2)),
                                    use_density = c(rep(TRUE, 10), TRUE, FALSE)) %>%
  mutate(case = 1:length(nbins)) %>%
  select(case, bin_continuous, nbins, quantile_bins, use_density)

@@

  # Specify the options to use with lime with no bins
  # hamby224_lime_no_bins_cases <- data.frame(bin_continuous = rep(FALSE, 2),
  #                                           quantile_bins = rep(TRUE, 2),
  #                                           nbins = rep(4, 2),
  #                                           use_density = c(TRUE, FALSE)) %>%
  #   mutate(case = 1:length(nbins)) %>%
  #   select(case, bin_continuous, nbins, quantile_bins, use_density)
  # 
  # # Run the lime functions for the specified number of bins
  # hamby224_no_bins_results <- pmap(.l = as.list(hamby224_lime_no_bins_cases[,-1]),
  #          .f = run_lime, # run_lime is one of my helper functions
  #          train = hamby173and252_train %>% select(rf_features),
  #          test = hamby224_test %>% arrange(case) %>% select(rf_features) %>% na.omit(),
  #          rfmodel = as_classifier(rtrees),
  #          label = "TRUE",
  #          nfeatures = 3)

  # # Separate the lime and explain function results
  # hamby224_lime_no_bins <- map(hamby224_no_bins_results, function(list) list$lime)
  # hamby224_explain_no_bins <- map_df(hamby224_no_bins_results, function(list) list$explain)
  # 
  # # Bind the lime dataframes with bin_continuous TRUE and FALSE
  # hamby224_lime <- c(hamby224_lime, hamby224_lime_no_bins)
  # hamby224_explain <- bind_rows(hamby224_explain, hamby224_explain_no_bins)

@@

@@

```{r}
hamby224_lime_results %>%
  mutate(bc_qb = as.character(factor(bin_continuous):factor(quantile_bins)),
         nbins_update = factor(ifelse(bin_continuous == FALSE, "0", nbins))) %>%
  ggplot(aes(x = nbins_update, y = mse, color = bc_qb)) +
  geom_point() + 
  facet_grid( ~ set) + 
  theme_bw()
```

@@

Ideas for improvement of LIME: 
  - change the binning method:
    - lime is not good with linear relationships with classifiers due to the 
    inside-outside binning - it would be better to use a cumulative approach
  - consider interactions in the ridge regression model
  - learn lambda in the ridge regression
  - could add a penalty for the number of parameters in the model (or the number of bins)
  - could start with a fine grid of bins and then go backwards and fit the models on this sampled data
  - could try a type of ANOVA test if we can have nested models or if we can assume nesting
  - could compute something like an R^2_adj
